\documentclass[notes]{subfiles}

\begin{document}
	\chapter{Applications of Integration}
	\addcontentsline{toc}{section}{5.1 - Areas Between Curves}
	\setcounter{section}{1}
	\fancyhead[RO,LE]{\bfseries \large\nameref{cs51}} 
	\fancyhead[LO,RE]{\bfseries \currentname}
	\fancyfoot[C]{{}}
	\fancyfoot[RO,LE]{\large \thepage}	%Footer on Right \thepage is pagenumber
	\fancyfoot[LO,RE]{\large Chapter 5.1}
	
\section*{Areas Between Curves}\label{cs51}
	\subsection*{Before Class}
	\addcontentsline{toc}{subsection}{Before Class}
	\subsubsection*{Area}
	\addcontentsline{toc}{subsubsection}{Area}
		\begin{ex}
			Let $f(x) =-(x-1)^2+3$ and $g(x) = 1$, graphed below.\\
			\begin{center}
				\begin{tikzpicture}
					\begin{axis}[
						every tick label/.append style={font=\small},
						axis x line = middle,
						axis y line = middle,
			    			every axis y label/.style={at={(ticklabel cs:1.15)}},
			    			%ytick = {-4, -2, -3, -1, 1, 2, 3, 4},
						y label style={at={(axis description cs:.25,1.15)},anchor=north},
			    			ylabel = {$f(x)$},
			    			ymin = -1.5, ymax = 4.5,
		    				every axis x label/.style= {at ={(ticklabel cs:1)}},
		    				%xtick = {-4,-3,-2,-1,1,2,3,4},
		    				x label style={at={(axis description cs:1.1,.25)},anchor=east},
		    				xlabel = {$x$},
		    				xmax = 3.5
					]
						\addplot[thick, domain = -1:3.5] {-1*(x-1)^2+3} node[midway, yshift = 18pt, xshift = -2pt] {$f(x)$};
						\addplot[thick, domain = -1:3.5] {1} node[midway, yshift = -10pt] {$g(x)$};
					\end{axis}
				\end{tikzpicture}
			\end{center}
			
			\begin{enumerate}[(a)]
				\item Write (and evaluate) an expression to find the area between $f(x)$ and the $x-$axis on $[0,2]$.  Shade the area on the graph.
					\vs{1}
					
					\newpage
					
				\item Write (and evaluate) an expression to find the area between $g(x)$ and the $x-$axis on $[0,2]$.  Shade the area on the graph.
					\vs{1}
				\item Write (and evaluate) an expression to find the area between $f(x)$ and $g(x)$ on $[0,2]$.  Do you need to shade the area?
					\vs{1}
			\end{enumerate}
		\end{ex}
						
		\begin{thm}[Area Between Curves]
			\showto{ins}{	
				Let $f,g$ be continuous functions, and let \fbox{$f(x)\geq g(x)$} 
					\[A = \int_a^b (f(x)-g(x))\,dx\]
			}
			\showto{st}{
				Let $f,g$ be continuous functions, and let \blank{2} for all $x$ in $[a,b]$.  The area $A$ of the region bounded by the curves $y = f(x)$, $y = g(x)$ and the lines $x=a$, $x=b$ is given by\vspace{.5in}
			}
		\end{thm}
			
		\begin{ex}
			Find the area of the region bounded above by $y = x^2+1$, below by $y = x$, and on the sides by $x = 0$ and $x = 1$
		\end{ex}
			\vs{1}
			\newpage
			
		\begin{ex}
			Find the area of the region enclosed by the parabolas $y = x^2$ and $y = 2x-x^2$
		\end{ex}
			\vs{1}

			
		\begin{ex}
			Find the area of the region bounded by the curves $y = \sin x$ and $y = \cos x$, from $x = 0$ to $x = \dfrac{\pi}{2}$
		\end{ex}
			\vs{1}
			\newpage
	
	\subsubsection*{Pre-Class Activities}
	\addcontentsline{toc}{subsubsection}{Pre-Class Activities}
		\begin{ex}
			Find the area of the region enclosed by the curves $y = x+1$ and $y = 9-x^2$ between $x = -1$ and $x=2$.
		\end{ex}
			\vs{1}
			
		\begin{ex}
			Find the area of the region enclosed by the curves $y = \sin x$ and $y = x$ between $x = \dfrac{\pi}{2}$ and $x = \pi$.
		\end{ex}
			\vs{1}
			
		\begin{ex}
			Find the area between the curves $y = (x-2)^2$ and $y = x$.
		\end{ex}
			\vs{1}
			\newpage
			
	\subsection*{In-Class}
	\addcontentsline{toc}{subsection}{In-Class}
	\subsubsection*{Examples}
	\addcontentsline{toc}{subsubsection}{Examples}
		
		\begin{ex}
			Sketch the region enclosed by the curves $y = \sqrt{x-1}$ and $y=x-1$, and find the area.
		\end{ex}
			\vs{1}
			
		
		\begin{ex}
			Sketch the region enclosed by the curves $y = x^2$ and $y = 4x-x^2$, and find the area.
		\end{ex}	
			\vs{1}

			\newpage
			
		\begin{ex}
			Find the area enclosed by the line $y = x-1$ and the parabola $y^2=2x+6$
		\end{ex}
			\vs{1}
			\newpage
			
		\begin{ex}
			Sketch the region enclosed by the curves $x = y^4$, $y=\sqrt{2-x}$, and $y = 0$, and find the area.
		\end{ex}
			\vs{1}

			
			
		\begin{ex}
			Find the area of the triangle with vertices $(2,0)$, $(0,2)$, and $(-1,1)$.
		\end{ex}	
			\vs{1}
			\newpage
			
		\begin{ex}
			Sketch the region enclosed by the curves $x = 2y^2$, $x = 4+y^2$, and find the area.
		\end{ex}
			\vs{1}

		
			\newpage
	
	\subsection*{After Class}	
	\addcontentsline{toc}{subsection}{After Class}
		\begin{ex}
			Find the area of the region bounded by $y = \sqrt{x}$, $y = x^{-2}$, and $x = 4$.
		\end{ex}
			\vs{1}
			
		\begin{ex}
			Sketch the region bounded by the curves $y = \cos \pi x$ and $y = 4x^2 - 1$ and then find the area of the region.
		\end{ex}
			\vs{1}

		
			\newpage
			
		\begin{ex}
			Sketch the region enclosed by $x = y - 1$, $y = 9-x^2$, $x = -1$, and $x = 2$, then find the area of the region.
		\end{ex}
			\vs{1}
			
		\begin{ex}
			Sketch the region enclosed by $y = \dfrac{1}{x^2}$, $y = x$, and $y = \dfrac{1}{8}x$, then find the area.
		\end{ex}
			\vs{1}
		
	\clearpage
\end{document}